HO unification from object language to meta language

### 2024-02-16 main.tex
wip abstract

We apply this technique to the implementation of a type-class solver for Coq,
which is a proof search procedure based on back-chaining designated lemmas.
Type-class solvers provide essential automation to widely used 
Coq libraries such as Stdpp/Iris~\cite{JUNG_KREBBERS_JOURDAN_BIZJAK_BIRKEDAL_DREYER_2018}
and TLC~\cite{10.1007/978-3-642-14052-5_15} that constitute our test bed.
\end{abstract}

>>>>

We apply this technique to the implementation of a type-class solver for Coq
in Elpi~\cite{dunchev15lpar} (a dialect of $\lambda$Prolog).
Type-class solvers
are proof search procedures based on back-chaining designated lemmas and
provide essential automation to widely used 
Coq libraries such as Stdpp/Iris~\cite{JUNG_KREBBERS_JOURDAN_BIZJAK_BIRKEDAL_DREYER_2018}
and TLC~\cite{10.1007/978-3-642-14052-5_15} that constitute our test bed.
\end{abstract}
